An upper bound to gas storage and delivery via pressure-swing adsorption in porous materials

### 2021-09-04 gas-adsorption/rsc-gas-ads-complete.tex
added discussion abt grav vs vol del cap

\startreferees{Deliverable capacity defined below}
For a vehicle employing a porous material to store natural gas or hydrogen, the
(volumetric) \emph{deliverable capacity} of the gas is the primary
thermodynamic property that determines the driving
range on a given ``full'' tank of fuel~\cite{mason2014evaluating}. 
The adsorbed gas storage tank delivers the
gaseous fuel to the engine via an (assumed) isothermal pressure
swing~\cite{sircar2002pressure}. The deliverable capacity (see
Fig.~\ref{fig:delcap}) is the density of the gas in the material at the storage
pressure $\pfull$ minus the residual gas that remains adsorbed at the lowest
pressure $\pempty$ such that sufficient flow is maintained to feed the engine.
For commercial feasibility, the US Department of Energy (DOE) has set
deliverable capacity targets for both adsorbed methane and hydrogen storage and
delivery for vehicles. For methane, the Advanced Research Projects
Agency--Energy (ARPA-E) set a deliverable capacity target of 315\ L STP CH$_4$
per L of adsorbent at 298 K using a 65\,bar to 5.8\,bar pressure
swing~\cite{simon2015materials}. For hydrogen, the DOE set a series of
progressive targets at five year intervals, with the ultimate target of 0.05\,kg
H$_2$/L~\cite{h2targetsDOE} using a 100\ bar to 5\ bar pressure swing at a
minimum of -40 $^\circ$C~\cite{allendorf2018assessment}. Thus far, despite the
emergence of highly tunable materials with large surface areas, such as
metal-organic frameworks~\cite{furukawa2013chemistry} and covalent organic 
frameworks~\cite{diercks2017atom}, no porous material has met these deliverable capacity targets.

@@

\startreferees{Flexible MOFs section added below}
\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{figs/two-phase}
    \caption{Cartoon of a two-phase, collapsing material. The material can exist in two phases: an open phase in which gas molecules can adsorb, and a closed phase that is collapsed and cannot fit any gas molecules. Take the closed phase as more stable, so that the material can collapse and expel residual gas.
    The pressure of gas at which the structural transition occurs depends on the gas-host interactions and relative stability of the phases. We wish for the structural transition to occur between $\pfull$ and $\pempty$.
    }
    \label{fig:flexible-cartoon}
\end{figure}

@@

\startreferees{Explain how the point of our paper is not to find structure-property relationships.}

Several studies elucidated relationships between structural features of nanoporous materials---such as void fraction, pore size, and surface area---and their deliverable capacity of various gases \cite{gomez2014exploring,ahmed2019exceptional,simon2015materials,moghadam2018computer,Tong2018}. 
Such structure-property relationships serve as useful heuristics for designing new materials with high deliverable capacity. However, the intention of our paper is not to discover structure-property relationships. 
Rather, we place our upper bound on the deliverable capacity of [rigid] materials that holds irrespective of how the structural features of the material are tuned.

@@

>>>>

For a vehicle employing a porous material to store natural gas or hydrogen, the
(volumetric) \emph{deliverable capacity} of the gas is the primary
thermodynamic property that determines the driving
range on a given ``full'' tank of fuel~\cite{mason2014evaluating}. 
The adsorbed gas storage tank delivers the
gaseous fuel to the engine via an (assumed) isothermal pressure
swing~\cite{sircar2002pressure}. The deliverable capacity (see
Fig.~\ref{fig:delcap}) is the density of the gas in the material at the storage
pressure $\pfull$ minus the residual gas that remains adsorbed at the lowest
pressure $\pempty$ such that sufficient flow is maintained to feed the engine.
For commercial feasibility, the US Department of Energy (DOE) has set
deliverable capacity targets for both adsorbed methane and hydrogen storage and
delivery for vehicles. For methane, the Advanced Research Projects
Agency--Energy (ARPA-E) set a deliverable capacity target of 315\ L STP CH$_4$
per L of adsorbent at 298 K using a 65\,bar to 5.8\,bar pressure
swing~\cite{simon2015materials}. For hydrogen, the DOE set a series of
progressive targets at five year intervals, with the ultimate target of 0.05\,kg
H$_2$/L~\cite{h2targetsDOE} using a 100\ bar to 5\ bar pressure swing at a
minimum of -40 $^\circ$C~\cite{allendorf2018assessment}. Thus far, despite the
emergence of highly tunable materials with large surface areas, such as
metal-organic frameworks~\cite{furukawa2013chemistry} and covalent organic 
frameworks~\cite{diercks2017atom}, no porous material has met these deliverable capacity targets.

@@

\begin{figure}
    \centering
    \includegraphics[width=0.95\columnwidth]{figs/two-phase}
    \caption{Cartoon of a two-phase, collapsing material. The material can exist in two phases: an open phase in which gas molecules can adsorb, and a closed phase that is collapsed and cannot fit any gas molecules. Take the closed phase as more stable, so that the material can collapse and expel residual gas.
    The pressure of gas at which the structural transition occurs depends on the gas-host interactions and relative stability of the phases. We wish for the structural transition to occur between $\pfull$ and $\pempty$.
    }
    \label{fig:flexible-cartoon}
\end{figure}

@@

\startreferees{Explain how the point of our paper is not to find structure-property relationships.}
Several studies elucidated relationships between structural features of nanoporous materials---such as void fraction, pore size, and surface area---and their deliverable capacity of various gases \cite{gomez2014exploring,ahmed2019exceptional,simon2015materials,moghadam2018computer,Tong2018}. 
Such structure-property relationships serve as useful heuristics for designing new materials with high deliverable capacity. However, the intention of our paper is not to discover structure-property relationships. 
Rather, we place our upper bound on the deliverable capacity of [rigid] materials that holds irrespective of how the structural features of the material are tuned.

@@

\startreferees{Discuss gravimetric vs volumetric deliverable capacity}

For vehicular gas storage, gravimetric deliverable capacity (amount of gas per mass of material) may be considered as a material performance metric to avoid a heavy adsorbed-gas fuel tank. However, the volumetric deliverable capacity (amount of gas per volume of material) dominantly determines the driving range on a full fuel tank of a given volume \cite{mason2014evaluating}. That said, several articles have explored the tradeoff between gravimetric and volumetric deliverable capacity, particularly for hydrogen storage \cite{gomez2017understanding,chen2020balancing,goldsmith2013theoretical,ahmed2021predicting}.
